The Tor Network - Design and Defenses \\ \Large Computer Security 1 - CS5460 \\ \LaTeX{}

### 2013-12-10 paper.tex
expansion, finalization

% -------------------------------------------------------------------------------

@@

Attacks from adversaries against Tor can be classified into several categories: attack on the user, attacks on their computer, attacks on the Tor network itself, attacks on the exit's connection across the Internet, and attacks on the server. Tor's developers have implemented or recommended various defenses against common attacks on each of these layers.

@@

Human mistakes are one of the most serious threats to deanonymization, and defenses against it are outside the scope of the Tor project. While Tor users can enjoy a reasonable level of anonymity and protection against traffic analysis, use of the Tor network is useless if information about their identity and/or location is leaked to the Internet. The electronic trail they leave behind can be used to completely deanonymize them and reveal their activities. The Tor Project provides recommendations that aim to prevent users from leaking their identity, but actual defenses against this attack are generally outside the scope of Tor.

(notable examples, describe defenses)

@@

Tor users can also be revealed or have their privacy compromised by their own workstations. If their computer contains spyware, backdoors, or other malicious software that can be used to identify them or their traffic, then a user may be tricked into believing that they are anonymous when in fact they are not.

(going to expand this a bit more, discuss Javascript vs NoScript, cross-site scripting attacks, TBB defenses)

@@

Exit nodes are valuable on the Tor network due to their necessity for the final hop of the circuit and because they are rarer than traditional relays. Exit node operators typically have to deal with ISP complaints for any nefarious Internet activities performed by the users at the other end of the circuit. Although these complaints can be largely combated by implementing a reduced exit policy, there are 912 exit notes at the time of this writing, 19.74\% of the total 4,737 relays on the Tor network. It is entirely possible than an adversay could control an exit node, giving them insight into the traffic leaving Tor. If the traffic is encrypted, the exit node could still see the DNS lookup and HTTP headers. If encryption is not implemented, all traffic would thus be available for inspection.

In September 2007, Swedish security consultant Dan Egerstad operated five exit nodes and monitored their traffic. Over the course of his experiment, he obtained the usernames and passwords for over 100 email accounts, read the correspondence from embassies in Australia, Japan, Iran, India, and Russia, along with communication between dignitaries including the Indian ambassador to China, various politicians in Hong Kong, workers in the Dalai Lama's liaison office, and several human-rights groups in Hong Kong. He also obtained sensitive spreadsheets and documents about military and political activities. Egerstad's analysis further revealed that approximately 95\% of the traffic flowing over his nodes was not encrypted.\cite{Wired2007}

An adversary could operate one or more exit nodes, as Egerstad did, or they could wiretap the exit's traffic and gain access to the traffic that way, perhaps without the knowledge of the exit operator. While the exit has no knowledge of the entire circuit and thus cannot deduce the origin of the traffic, the unencrypted traffic can be quite revealing and problematic, as Egerstad demonstrated. The primary way that Tor combats this through encryption. The Tor Browser Bundle comes with the HTTPS Everywhere, which prefers the use of HTTPS when connecting to web servers. Most email servers also support SSL/TLS, and users can also manually encrypt their documents or emails using PGP. Although Tor has no way of enforcing this final layer of encryption, it highly recommends it and places notices about this on many places on its website.

@@

The web server can also be a point of failure for the privacy and anonymity of the end user.

(going to expand this a bit more. Does the web server support SSL/TLS? The adversary could fake masquerade as the server)

@@

Although it is popular, a number of practical attacks and weaknesses have been demonstrated against its Key Scheduling Algorithm and PRNG that call into question RC4's security. In November 2013, Microsoft recommended disabling RC4 from TLS wherever possible.

@@

Another potential method to de-anonymize users is through active watermarking of packets. Digital watermarks require less time deploy, often have a higher success rate, and do not require observing traffic for long periods of time. If an attacker can modify the traffic flow such that it is noticable at the other end of Tor, then it becomes easy to identify end users and correlate them with their activities.

@@

Earlier this year, Edward Snowden revealed that the United States National Security Agency (NSA) has been attempting to penetrate the Tor network and de-anonymize its users, but with little success. In a June 2012 PowerPoint presentation titled ``Tor Stinks'', the NSA stated that ``with manual analysis we can de-anonymize a \textit{very small fraction} of Tor users'' but admitted that they have had no success in identifying a user on demand, and that they will never be able to de-anonymize all Tor users all the time. However, they had performed research on a variety of attacks against Tor. Their purpose was reveal ``terrorists'' and other individuals of interest to the United States.

@@

(going to expand this a bit more and devote the couple pages to this section. I've got IEEE citations like \cite{Xin2009}, \cite{Ling2011}, and \cite{Ling2012} that should be very helpful in demonstrating some weaknesses of Tor

Bauer and McCoy, \textit{et al}, described a low-resource routing attack against the Tor network.\cite{Bauer2007}

@@

However, Tor is not impenetrable. By far the most significant threat to Internet anonymity is carelessness: a user may publish enough electronic clues that point to their real-life identity. By design, Tor cannot defend against this. The most effective attacks against Tor itself have used exploits in the Tor Browser Bundle, Javascript, or the host operating system. These indirect attacks have been used in the past to successfully de-anonymize a few of its users. In other cases, traditional detective work has been used to take down hidden services inside the Tor network. However, in general the Tor routing protocol has proven fairly secure, with only a handful of theoretical attacks published and tested by researchers in the field. As Tor's documentation suggests, it is not a foolproof solution for online anonymity, and users must still be careful with their information.

>>>>

@@

While Tor aims to provide anonymity and privacy on the Internet, adversaries can attack these goals on several fronts. The user might make mistakes or could be phished into leaving o revealing information online. An adversary might also use malware such as keyloggers to wiretap at the source. If they have control over multiple relays or parts of the Tor network they could also performing such as digital watermarks, timing attacks, or other network-level exploits. These could be used to correlate traffic heading in and out of the Tor network, thus revealing the identity and activities of end users. Attackers who are more interested in the traffic rather than its origin might wiretap or run a compromised exit relay. Any unencrypted traffic could contain sensitive information. Compromised web servers could recognize connections from known Tor exit nodes and inject Javascript attacks or deny them service. These are all possible attacks against the anonymity and privacy that Tor provides.

@@

Human mistakes are one of the most serious threats to deanonymization, and defenses against it are outside the scope of the Tor project. While Tor users can enjoy a reasonable level of anonymity and protection against traffic analysis, this can be rendered useless if information about their identity and/or location is leaked to the Internet. The electronic trail users leave behind can be used to completely deanonymize them and reveal their activities. The Tor Project recommends against providing names or other identifying information in web forms, but defenses against this are outside the scope of proxies, VPNs, and Tor.

@@

Spyware, backdoors, and other malicious software can compromise the anonymity and privacy of Tor users before their web traffic is sent through Tor. If an attacker can silently install or execute the malware on the user's system through Tor then they may be able to reveal the user's IP address or compromise their system completely. There have been several instances where this has been done in the past.

In February 2012, activists in Iran and Syria were targeted by keyloggers and backdoors designed to gather sensitive information and provide access to their computer system. The files were distributed by email; the keylogger was disguised as a Microsoft PowerPoint, and the backdoor as a image file trojan horse. Both pieces of malware modified the Windows startup script to ensure that they were silently launched in the background. This malware bypassed the Tor Browser Bundle and sent logged keystrokes to a server operated by the Syrian government.

In September 2013, the FBI used malware to deanonymize Tor users. Several days before the Freedom Hosting hidden service was taken down, the FBI configured the server to deliver malicious Javascript that exploited a critical memory management vulnerability in Tor Browser Bundle. The Javascript payload also included a small Windows executable that sent the victim's MAC address and hostname to an FBI server in Virginia but did no other function. The vulnerability only affected older versions of Firefox (and thus older versions of the Tor Browser Bundle) as the security hole had been fixed upstream three months prior to the attack. The FBI had used the exploit sparingly since 2002. The code was in place for less than a day before visitors discovered it and published it on the Internet for analysis.

Tor combats this threat on several levels. First, the Tor Browser Bundle is pre-installed with the NoScript extension, which only loads scripts from whitelisted sources. Secondly, the developers keep the TBB updated to the latest version of Firefox and supply their own security enhancements. Finally, Tor offers the Tails operating system. Tails is based on Debian GNU/Linux, forces all outbound traffic to use Tor, and runs on a ramdisk so that the system is reset on reboot. Firefox, the Tor Browser Bundle, and Tails are all updated frequently, making it very difficult for adversaries to launch attacks that are effective on a wide scale.

@@

Exit nodes are valuable on the Tor network due to their necessity for the final hop of the circuit and because they are rarer than traditional relays. Exit node operators typically have to deal with ISP complaints for any nefarious Internet activities performed by the users at the other end of the circuit. Although these complaints can be largely combated by implementing a reduced exit policy, there are 912 exit notes at the time of this writing, 19.74\% of the total 4,737 relays on the Tor network. It is entirely possible than an adversary could control an exit node, giving them insight into the traffic leaving Tor. If the traffic is encrypted, the exit node could still see the DNS lookup and HTTP headers. If encryption is not implemented, all traffic would thus be available for inspection.

In September 2007, Swedish security consultant Dan Egerstad operated five exit nodes and monitored their traffic. Over the course of his experiment, he obtained the usernames and passwords for over 100 email accounts, read the correspondence from embassies in Australia, Japan, Iran, India, and Russia, along with communication between dignitaries including the Indian ambassador to China, various politicians in Hong Kong, workers in the Dalai Lama's liaison office, and several human-rights groups in Hong Kong. He also obtained sensitive spreadsheets and documents about military and political activities. Egerstad's analysis further revealed that approximately 95\% of the traffic flowing over his nodes was not encrypted during the course of his 2007 experiment.\cite{Wired2007}

An adversary could operate one or more exit nodes, as Egerstad did, or they could wiretap the exit's traffic and gain access to the exit's traffic without the knowledge of the exit operator. While the exit has no knowledge of the entire circuit and thus cannot deduce the origin of the traffic, the unencrypted traffic can be quite revealing and problematic, as Egerstad demonstrated. The primary way that Tor combats this through encryption. The Tor Browser Bundle comes with the HTTPS Everywhere, which prefers the use of HTTPS when connecting to web servers. Most email servers also support SSL/TLS, and users can also manually encrypt their documents or emails using PGP. The Tails OS and many other Linux distributions come with GnuPG pre-installed. Although Tor has no way of enforcing this final layer of encryption, it recommends frequently on its website.

@@

The web server can also be a point of failure for the privacy and anonymity of the end user. Compromised servers could recognize incoming connections from known Tor exit nodes and offer malicious software for Tor users. They could also block Tor completely, (as Facebook did during June 2013) or make the offered service slow or difficult to use. In the extreme case, the server could be masquerading as a another and offer a fake service in place of a legitimate one. This could be use for phishing, tricking the user into revealing identifying information.

This threat is not unique to Tor users. Web servers can be compromised in general. Authentication is typically performed with public key certificates issued by certificate authorities (CAs). Most popular browsers (e.g. Chrome, Firefox, IE, Opera, Safari, etc) come pre-loaded with the public key from these CAs and can thus verify the certificate presented by the server during the TLS handshake. The HTTPS extension in the Tor Browser Bundle prefers using TLS whenever available, preventing spoofing attacks for many common websites.

Users must solve a CAPTCHA before being able to do a search on Google due to high demand from the Tor exit nodes. Google maintains logs of search terms and can build user profiles based on their search terms. These records can compromise the privacy of Tor and non-Tor users and in some cases have been incriminating. To counter this, Tor recommends that users utilize an alternative and more private search engine. One of the most popular of these is DuckDuckGo. This search engine, traditionally offered at duckduckgo.com, also operates as a Tor hidden service, allowing users to search the Internet anonymously and without tracking. DuckDuckGo does not maintain records of user queries, they cannot be subpoenaed for user profiles or search history.

@@

Tor's security relies upon modern cryptography. If an adversary is able to compromise popular algorithms such as AES, Diffie-Hellman-Merkle, or the cipher suite agreed upon during the TLS handshake, they would be able to decrypt the traffic flowing over the Tor network.

Although attacks against AES that are computationally faster than a brute-force attack, none are computationally feasible with current resources. The Diffie-Hellman-Merkle key exchange is considered secure if the agreed upon parameters (i.e. the finite cyclic group G and a generating element g in G) are chosen properly. If they are, the most efficient public means to crack DH is to solve the discrete logarithm problem, for which no efficient algorithm is known to exist. RSA is based on the difficulty of factoring the product of two large prime numbers. There is currently no publically known algorithm for factoring integers that runs in polynomial time. These cryptography systems are generally considered secure.

However, there are some cryptographic attacks that may be possible by a well-resourced adversary. Tor and web servers in general are transitioning into ECC, and their security depends on the strength of the chosen elliptic curve. Poor choices for the curve may leave cryptographic backdoors and other weaknesses that could be exploited. Attacks could also be possible for other algorithms, such as RC4. A number of practical attacks against RC4's Key Scheduling Algorithm and PRNG call into question its security, and there is recent speculation that some cryptologic agencies may possess the ability to break RC4 when used in TLS. Microsoft recommends disabling RC4 wherever possible for these reasons.

The Tor Browser Bundle maintains a ciphersuite list for use during TLS with web servers and with Tor relays. The top six suites are TLS1\_ECDHE\_ECDSA\_WITH\_AES\_256\_CBC\_SHA, TLS1\_ECDHE\_RSA\_WITH\_AES\_256\_CBC\_SHA, TLS1\_DHE\_RSA\_WITH\_AES\_256\_SHA, TLS1\_DHE\_DSS\_WITH\_AES\_256\_SHA, TLS1\_ECDH\_RSA\_WITH\_AES\_256\_CBC\_SHA, TLS1\_ECDH\_ECDSA\_WITH\_AES\_256\_CBC\_SHA. These algorithms are widely considered to be very strong.

@@

Another potential method to deanonymize users is through active watermarking of packets. Digital watermarks require less time deploy, often have a higher success rate, and do not require observing traffic for long periods of time. If an attacker can modify the traffic flow such that it is noticable at the other end of Tor, then it becomes easy to identify end users and correlate them with their activities.

@@

Earlier this year, Edward Snowden revealed that the United States National Security Agency (NSA) has been attempting to penetrate the Tor network and deanonymize its users, but with little success. In a June 2012 PowerPoint presentation titled ``Tor Stinks'', the NSA stated that ``with manual analysis we can deanonymize a \textit{very small fraction} of Tor users'' but admitted that they have had no success in identifying a user on demand, and that they will never be able to deanonymize all Tor users all the time. However, they had performed research on a variety of attacks against Tor. Their purpose was reveal ``terrorists'' and other individuals of interest to the United States.

@@

Most of the attacks that are possible to use against Tor can also be used against other anonymization services such as proxies and VPNs, or even in general. Adversaries may use attacks such as social engineering, malware, wiretapping, web server exploits, digital watermarking, and cryptographic attacks against many other users, making these threats not unique to Tor itself but rather general threats across the overall Internet. For most uses though, Tor provides the best available protection against a well-resourced observer. However, simply routing multi-encrypted traffic through random circuits is not sufficient to provide complete computer and network security. By itself, Tor cannot protect against vulnerabilities in operating systems or in its software, but the open-source community has made these attacks very difficult to implement on a large scale in practice. Deanonymizing individual users via attacks on the Tor network itself is considered very difficult due to the sheer number of users using Tor, the scale of Tor, and the bandwidth that it carries. There are some vulnerabilities that can still be mitigated, and the Tor developers and the Internet community at large has been focused on improving security. This has been especially apparent in recent months in light of the NSA capability leaks by Edward Snowden.

@@

However, Tor is not impenetrable. By far the most significant threat to Internet anonymity is carelessness: a user may publish enough electronic clues that point to their real-life identity. By design, Tor cannot defend against this. The most effective attacks against Tor itself have used exploits in the Tor Browser Bundle, Javascript, or the host operating system. These indirect attacks have been used in the past to successfully deanonymize a few of its users. In other cases, traditional detective work has been used to take down hidden services inside the Tor network. However, in general the Tor routing protocol has proven fairly secure, with only a handful of theoretical attacks published and tested by researchers in the field. As Tor's documentation suggests, it is not a foolproof solution for online anonymity, and users must still be careful with their information.
